VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-28 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
spelling mistakes

\begin{theorem}
The mapping $h(x)$ is a strictly monotone continuous function. The function $h(x)$ is, therefore, invertable.
\end{theorem}

@@

\noindent
The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section~\ref{sec:rs}. The functions $g(x)$ and $f(x)$ now also need to be differentiable and invertable. Moreover, $a(0)$ must exist. These additional restrictions on $f(x)$ and $g(x)$ are assumed to be true for the remainder of the paper and as such are not repeated again. As will become apparent later, these additional restictions reduce the number of fractional integrals we can visualize with the framework we propose in Section~\ref{sec:rl_to_cav}. However, this fact does not diminish the importance of the proposed framework as it allows us to gain deeper insight into the process of fractional integration.

@@

\noindent
We can approximate the area of $R$ by using rectangular integration strips. It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that inscribe $R$. This can only be accomplished if the sides of the aforementioned integration strips are tranlsations of the function $a(y)$.\\

@@

\begin{equation}
\label{eq:rl_to_rs}
_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau), 
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
\widetilde{g}_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}
Moreover, the function $\widetilde{g}_t^{\alpha}(\tau)$ is invertable. Its inverse is:
\begin{equation}
\label{eq:h}
\widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
\end{equation}
The function $\widetilde{g}_t^{\alpha}$ is invertable, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$. Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The functions $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh} for $\alpha\in\mathsf{A}$.\\

@@

%\subsection{Podlubny's Geometric Interpretation}
\noindent
Podlubny also showed that we can assign a geometric meaning to the fractional integral in equation~\eqref{eq:rl_to_rs} by visualizing the equivalent Riemann-Stieltjes integral contained within the same equation \cite{bullock88,podlubny02}. Consider the axis $\tau$, $\widetilde{g}_t^{\alpha}$ and $f(\tau)$. Podlubny suggests that we build a ``fence'' in $(\tau,\widetilde{g}_t^{\alpha},f)$-space. The base of the aforementioned fence is given by the curve $(\tau,\widetilde{g}_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,\widetilde{g}_t^{\alpha}(\tau),f(\tau))$. The ``shadow'' of this fence, i.e. the area under the curve which is obtained by projecting this fence onto the $\widetilde{g}f$-plane corresonds to the value which is obtained when equation~\eqref{eq:rl_to_rs} is evaluated. As an example, the geometric interpretation so obtained for the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{fig:vis_old}.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{vis_old.pdf}
\caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
As is indicated in the figure, the graphs contained in each row of the subfigure-grid are obtained by varying $\alpha$, while the graphs contained in each column of the subfigure-grid are obtained by varying $t$. The fence in each subfigure is depicted in green. The areas depicted in red (the shadow of the fence) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.  The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively (in each subfigure). The intersection between the blue and cyan surfaces in each subfigure represents the curve that determines the height of the fence in each subfigure (it is depicted as a dashed curve).   
}
\label{fig:vis_old}
\end{figure}

@@

\noindent
Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(\tau)$ and the $\tau$-axis. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_t^{\alpha}$. Equation~\eqref{eq:rl_to_c} implies that when we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$. In other words, when we evaluate equation~\eqref{eq:rl_to_c} we are actually summing together the area of an infinite number of non-rectangular infinitesimals inscribing $R_t^{\alpha}$. The aforementioned infinitesimals are, however, non-static, since they need to be translations of $a_t^{\alpha}(y)$. The shape of these infitesimals are thus dependend on $\alpha$ and $t$. In summary, we can obtain a novel geometric interpretation of 
$_{a'}I_t^{\alpha}\,f(t)$ by first converting it into a Cavalieri integral. We will take the liberty in this paper to refer to the depiction of the aformentioned Cavalieri integral as the non-static non-rectangular sum-based geometric interpretation of $_{a'}I_t^{\alpha}\,f(t)$.\\

@@

\noindent
We can interpret equation~\eqref{eq:ex1} as the value which is obtained when we sum together the area of an infinite number of non-rectangular infinitesimals inscribing $R_{t}^{\alpha}$. The value so obtained is $A_{t}^{\alpha}$ (see Section~\ref{sec:rl_to_cav}). Note that, the infinitesimals that are used in the aformentioned sum are translations of $R_{t}^{\alpha}$'s right edge. The following observations can now be made by inspecting Figure~\ref{fig:geo1}: 
\begin{description}
 \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Figure~\ref{fig:geo1} are not equal to one another, i.e. $b_{t}^{\alpha_1}(y)\neq b_{t}^{\alpha_2}(y)$ when $\alpha_1\neq\alpha_2$. 
 \item[Effect of $t$] Note that the dashed grey-tinted curves in the right-most panel of Figure~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$. The dashed gray-tinted curves and the solid gray-tinted curves in the right-most panel are not equal to one another. The gray-tinted solid curves depicted in each of the panels of Figure~\ref{fig:geo1} are, therefore, not translations of one another. 
\end{description}
The following can thus be concluded: the value of both $\alpha$ and $t$ alters the shape of the aforementioned infinitesimals. Interestingly, their shape is more affected by $\alpha$ than by $t$. The curves in Figure~\ref{fig:geo1} that are associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature (if their 
sizes are ignored). The curves in Figure~\ref{fig:geo1} associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another.\\

@@

\section{Conclusion}
\noindent
In this paper we presented a novel geometric interpretation of the left-sided 
Riemann-Liouville fractional integral. It can be interpreted as the value which is 
obtained by summing toghether the area of an infinite number of non-static non-rectangular infinitesimals. The shape of the infinitesimals used within the aforementioned sum depend on the order of integration and the upper integration limit of the fractional integral being evaluated.

>>>>

\begin{theorem}
The mapping $h(x)$ is a strictly monotone continuous function. The function $h(x)$ is, therefore, invertible.
\end{theorem}

@@

\noindent
The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the beginning of Section~\ref{sec:rs}. The functions $g(x)$ and $f(x)$ now also need to be differentiable and invertible. Moreover, $a(0)$ must exist. These additional restrictions on $f(x)$ and $g(x)$ are assumed to be true for the remainder of the paper and as such are not repeated again. As will become apparent later, these additional restrictions reduce the number of fractional integrals we can visualize with the framework we propose in Section~\ref{sec:rl_to_cav}. However, this fact does not diminish the importance of the proposed framework as it allows us to gain deeper insight into the process of fractional integration.

@@

\noindent
We can approximate the area of $R$ by using rectangular integration strips. It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that inscribe $R$. This can only be accomplished if the sides of the aforementioned integration strips are translations of the function $a(y)$.\\

@@

\begin{equation}
\label{eq:rl_to_rs}
_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau), 
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
\widetilde{g}_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}
Moreover, the function $\widetilde{g}_t^{\alpha}(\tau)$ is invertible. Its inverse is:
\begin{equation}
\label{eq:h}
\widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
\end{equation}
The function $\widetilde{g}_t^{\alpha}$ is invertible, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$. Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The functions $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh} for $\alpha\in\mathsf{A}$.\\

@@

%\subsection{Podlubny's Geometric Interpretation}
\noindent
Podlubny also showed that we can assign a geometric meaning to the fractional integral in equation~\eqref{eq:rl_to_rs} by visualizing the equivalent Riemann-Stieltjes integral contained within the same equation \cite{bullock88,podlubny02}. Consider the axis $\tau$, $\widetilde{g}_t^{\alpha}$ and $f(\tau)$. Podlubny suggests that we build a ``fence'' in $(\tau,\widetilde{g}_t^{\alpha},f)$-space. The base of the aforementioned fence is given by the curve $(\tau,\widetilde{g}_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,\widetilde{g}_t^{\alpha}(\tau),f(\tau))$. The ``shadow'' of this fence, i.e. the area under the curve which is obtained by projecting this fence onto the $\widetilde{g}f$-plane corresponds to the value which is obtained when equation~\eqref{eq:rl_to_rs} is evaluated. As an example, the geometric interpretation so obtained for the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{fig:vis_old}.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{vis_old.pdf}
\caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
As is indicated in the figure, the graphs contained in each row of the subfigure-grid are obtained by varying $\alpha$, while the graphs contained in each column of the subfigure-grid are obtained by varying $t$. The fence in each subfigure is depicted in green. The areas depicted in red (the shadows of the fences) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.  The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively (in each subfigure). The intersection between the blue and cyan surfaces in each subfigure represents the curve that determines the height of the fence in each subfigure (it is depicted as a dashed curve).   
}
\label{fig:vis_old}
\end{figure}

@@

\noindent
Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(\tau)$ and the $\tau$-axis. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_t^{\alpha}$. Equation~\eqref{eq:rl_to_c} implies that when we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$. In other words, when we evaluate equation~\eqref{eq:rl_to_c} we are actually summing together the area of an infinite number of non-rectangular infinitesimals inscribing $R_t^{\alpha}$. The aforementioned infinitesimals are, however, non-static, since they need to be translations of $a_t^{\alpha}(y)$. The shape of these infinitesimals are thus dependent on $\alpha$ and $t$. In summary, we can obtain a novel geometric interpretation of 
$_{a'}I_t^{\alpha}\,f(t)$ by first converting it into a Cavalieri integral. We will take the liberty in this paper to refer to the depiction of the aforementioned Cavalieri integral as the non-static non-rectangular sum-based geometric interpretation of $_{a'}I_t^{\alpha}\,f(t)$.\\

@@

\noindent
We can interpret equation~\eqref{eq:ex1} as the value which is obtained when we sum together the area of an infinite number of non-rectangular infinitesimals inscribing $R_{t}^{\alpha}$. The value so obtained is $A_{t}^{\alpha}$ (see Section~\ref{sec:rl_to_cav}). Note that, the infinitesimals that are used in the aforementioned sum are translations of $R_{t}^{\alpha}$'s right edge. The following observations can now be made by inspecting Figure~\ref{fig:geo1}: 
\begin{description}
 \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Figure~\ref{fig:geo1} are not equal to one another, i.e. $b_{t}^{\alpha_1}(y)\neq b_{t}^{\alpha_2}(y)$ when $\alpha_1\neq\alpha_2$. 
 \item[Effect of $t$] Note that the dashed grey-tinted curves in the right-most panel of Figure~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$. The dashed gray-tinted curves and the solid gray-tinted curves in the right-most panel are not equal to one another. The gray-tinted solid curves depicted in each of the panels of Figure~\ref{fig:geo1} are, therefore, not translations of one another. 
\end{description}
The following can thus be concluded: the value of both $\alpha$ and $t$ alters the shape of the aforementioned infinitesimals. Interestingly, their shape is more affected by $\alpha$ than by $t$. The curves in Figure~\ref{fig:geo1} that are associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature (if their 
sizes are ignored). The curves in Figure~\ref{fig:geo1} associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another.\\

@@

\section{Conclusion}
\noindent
In this paper we presented a novel geometric interpretation of the left-sided 
Riemann-Liouville fractional integral. It can be interpreted as the value which is 
obtained by summing together the area of an infinite number of non-static non-rectangular infinitesimals. The shape of the infinitesimals used within the aforementioned sum depend on the order of integration and the upper integration limit of the fractional integral being evaluated.
